Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
first SR by hand

  group_by(
    sequenceID
    ) %>%
  mutate(
    course_past = Reduce(
      f = paste, 
      x = course_current, 
      accumulate = TRUE
      ) %>%
      lag
    ) %>%

@@

### Courses that were taken before each course
```{r}
d_past_student_course <- d_cumulative_transcript %>%
  select(sequenceID, eventID, item, course_past) %>%
  unnest(item, .drop=F)

d_past_course <- expand.grid(

  # Expand along students (sequenceID) and courses (itemID)
  sequenceID = unique(d_transactions$sequenceID),
  item       = unique(d_transactions$item),
  stringsAsFactors = FALSE
  ) %>%
  full_join(d_past_student_course, by= c("sequenceID", "item")) %>%  #ATTENTION: Duplicates resits. Adds values per retake of course (eg.10177849 SCI3048)
  arrange(sequenceID) %>%
  ungroup() %>%
  drop_na(eventID) %>%
  unnest(course_past) %>%
  distinct() %>%
  group_by(item) %>%
  summarise(full_past = paste( course_past, collapse = " ")) %>% #difference, between this and above?
  mutate(full_past    = str_split(full_past, pattern = " "),
         full_past    = map(.f= unique, .x=full_past),
         total_past_courses = map(.f=length, .x=full_past))
```

>>>>

  group_by(
    sequenceID
    ) %>%
  mutate(
    course_past = Reduce(
      f = c, 
      x = course_current, 
      accumulate = TRUE
      ) %>%
      lag(
        default = as.character(NA)
        )
    ) %>%

@@

```{r}

#
# SR by hand

# rhs = current course
d_transcript_cum_current <- d_transcript_cum %>%
  unnest(
    course_current,
    .drop = FALSE
    ) %>%
  rename(
    rhs = course_current
    )

# lhs = course past
d_transcript_cum_current %>%
  filter(!is.na(course_past)) %>%
  unnest(
    course_past,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_past
    ) %>%
  count(
    lhs, 
    rhs
    )

# lhs = course not so far
d_transcript_cum_current %>%
  unnest(
    course_not_so_far,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_not_so_far
    ) %>%
  count(
    lhs, 
    rhs
    )
```
